Verifying Demonstrations

### 2017-06-01 DataAuthenticity.tex
Edits data authenticity

\Cref{CreatedAfterStart} is more difficult to achieve.
In the above scenario, there is nothing that prevents Alice from submitting an 
older photo which is spatially related to the event.
In the security field \cref{CreatedAfterStart} is captured by a property called 
\emph{freshness}.
The freshness property is usually achieved by requiring that the data depend on
an unpredictable value.
The unpredictable value is commonly a value chosen randomly by the verifier, 
but there are ways to do this without the verifier too --- the basic 
requirement is that it is not under the prover's control, i.e.\ Alice in this 
scenario.
The idea is illustrated by the following example: we require Alice to include 
the front-page of a particular newspaper in the photo, since the exact 
front-page is difficult for Alice to predict in advance.
This particular example would of course not work in practice, since Alice can 
manipulate the photo afterwards to superimpose the required newspaper 
front-page\footnote{%
  There is, however, a subfield of digital forensics that works with image 
  manipulation detection, so there are methods that would prevent at least 
  Alice's easiest manipulation attempts.
}.
But this illustrates another important requirement for freshness: that the 
operation binding the unpredicatble value to the data must be difficult to redo 
later to change the value.

>>>>

\Cref{CreatedAfterStart} is more difficult to achieve.
In the above scenario, there is nothing that prevents Alice from submitting an 
older photo which is spatially related to the event --- i.e.\ to ensure 
\cref{CreatedAfterStart} we must ensure some sort of freshness.
% XXX Verify that this can be done using Fiat-Shamir heuristic
This can (probably) be solved using the Fiat--Shamir 
heuristic~\cite{FiatShamirHeuristic} (or something similar).
The main idea is that the operation binding the unpredictable value to the data 
must be difficult to redo later to change the value.

Instead of a photo, we will use \acp{LP}, more specifically, we will use 
\ac{PROPS}.
This will allow us to fulfil \cref{SpatiallyRelated}.
Since a location proof is a cryptographic value, it is easier to adapt it to 
fulfil \cref{CreatedAfterStart} too (compared to a photo).
